### 2017-12-08 1/exams/f-practice.tex
Solution for practice final.

@@

(check-expect (update "a" "b" '()) (list (list "a" "b")))
(check-expect (update "a" "c" (list (list "a" "b")))
              (list (list "a" "c")))
(check-expect (update "a" "e" (list (list "c" "b") (list "a" "d"))) 
              (list (list "c" "b") (list "a" "e")))
(define (update w m d)
  (cond [(empty? d) (list (list w m))]
        [(cons? d)
         (if (string=? (first (first d)) w)
             (cons (list w m) d)
             (cons (first d) (lookup w (rest d))))]))

@@

(: raekwon : \censor{[Listof Number] -> Boolean                         })

@@

(: ghostface : \censor{[X Y] [Listof X] [X -> Y] -> [Listof Y]          })

@@

In the accumulator version, after all elements of the list have been
seen, the first accumulator would be $330 = 80+70+2\times 90$) and
the second accumulator would be $4 =1+1+2$.

@@

;; Alt: define w-total function for denominator

;; w-total : [Listof Number] -> Number
;; Total a list of weights
(define (w-total ws)
  (cond [(empty? ws) 0]
        [(cons? ws)
         (+ (first ws) 
            (w-total (rest ws)))]))
\end{SaveVerbatim}

@@

(define (tree-elems bt)
  (tree-fold (lambda (x l r) (cons x (append l r))) '() bt))

@@

@@

\begin{verbatim}
;; all-paths : Graph String String -> [Listof Path]
;; Produce all non-cyclic paths from src to dst in g.
;; Assume: both nodes exist in graph.
(define (all-paths g src dst) '())
\end{verbatim}

@@

\noindent
Note: this function is tricky to test since the tests shouldn't
specify the order of the paths in the list.  You may ignore this
subtly and just write tests as though a {\tt check-expect} will pass
if the checked and expected expressions produce lists with the same
elements in any order, e.g. {\tt (check-expect (list 1 2) (list 2 1))}
would pass.

\newpage
[Space for problem 8.]
\end{document}

>>>>

\vskip 2.5in

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:
(cond [(> T 3) (q 4)] [else 9])           -->[const]
          ^
(cond [(> 7 3) (q 4)] [else 9])           -->[arith]
       ^^^^^^^
(cond [#true (q 4)] [else 9])             -->[cond]
^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
(q 4)                                     -->[plug]
^^^^^
(sqr 4)                                   -->[arith]
^^^^^^^
16
\end{SaveVerbatim}

\censor{\vspace{-2.5in}}
\censor{%
\noindent\BUseVerbatim{VerbEnv}}

@@

(check-expect (update "a" "b" '()) (list (list "a" "b")))
(check-expect (update "a" "c" (list (list "a" "b")))
              (list (list "a" "c")))
(check-expect (update "a" "e" (list (list "c" "b") (list "a" "d"))) 
              (list (list "c" "b") (list "a" "e")))
(define (update w m d)
  (cond [(empty? d) (list (list w m))]
        [(cons? d)
         (if (string=? (first (first d)) w)
             (cons (list w m) (rest d))
             (cons (first d) (update w m (rest d))))]))
\end{SaveVerbatim}

@@

(: raekwon : \censor{[Listof Real] -> Boolean                           })

@@

(: ghostface : \censor{(All [X Y] [Listof X] [X -> Y] -> [Listof Y])    })

@@

In the accumulator version, after all elements of the list have been
seen, the first accumulator would be $330 = 80+70+2\times 90$ and
the second accumulator would be $4 =1+1+2$.

@@

(define (w-avg xs ws) (w-avg/a xs ws 0 0))

;; w-avg/a : [Listof Number] [Listof Number] Number Number -> Number
;; Compute weighted average with accumulators:
;;  - sum-wxs: sum of weighted elements seen so far
;;  - sum-ws: sum of weights
(define (w-avg/a xs ws sum-wxs sum-ws)
  (cond [(empty? xs) (/ sum-wxs sum-ws)]
        [(cons? xs)
         (w-avg/a (rest xs) 
                  (rest ws)
                  (+ (* (first xs) (first ws)) sum-wxs)
                  (+ (first ws) sum-ws))]))
\end{SaveVerbatim}

@@

(define (tree-count bt)
  (tree-fold (lambda (x l r) (add1 (+ l r))) 0 bt))

@@

;; A DNA is a [Listof DNA-Base]
;; A RNA is a [Listof RNA-Base]
;; A DNA-Base is one of: "C", "G", "A", "T"
;; A RNA-Base is one of: "C", "G", "A", "U"

;; trans : DNA -> RNA
;; Transcribe DNA into RNA
(check-expect (trans '()) '())
(check-expect (trans (list "T" "A" "C" "T" "G"))
              (list "U" "A" "C" "U" "G"))
(define (trans dna)
  (map (lambda (db) (if (string=? db "T") "U" db)) dna))    
\end{SaveVerbatim}

@@

\begin{verbatim}
;; all-paths : Graph String String -> [Listof Path]
;; Produce all non-cyclic paths from src to dst in g.
;; Assume: both nodes exist in graph.
(define (all-paths g src dst) '())

(define G
  (list (list "a" (list "b" "c"))
        (list "b" (list "a" "d"))
        (list "c" (list "d"))))

(check-expect (all-paths G "a" "a")
              (list (list "a")))
(check-expect (all-paths G "a" "d")
              (list (list "a" "b" "d")
                    (list "a" "c" "d")))
(check-expect (all-paths G "a" "d")
              (list (list "a" "b" "d")
                    (list "a" "c" "d")))
\end{verbatim}

@@

\noindent
Note: this function is tricky to test since the tests shouldn't
specify the order of the paths in the list.  You may ignore this
subtly and just write tests as though a {\tt check-expect} will pass
if the checked and expected expressions produce lists with the same
elements in any order, e.g. {\tt (check-expect (list 1 2) (list 2 1))}
would pass.  (Tests are provided above, you don't need to add more unless
it's useful to you.)

\newpage
[Space for problem 8.]

(define (all-paths g src dst)
  (all-paths/seen g src dst '()))

;; all-paths/seen : Graph String String [Listof String] -> [Listof Path]
;; Accumulator: list of nodes visited so far on path
;; Termination: each recursive call adds an item to seen list not previously
;; seen.  Since there are finite nodes, we get closer to trivial case:
;; src is in seen.
(define (all-paths/seen g src dst seen)
  (cond [(string=? src dst) (list (list src))]
        [(member? src seen) '()]
        [else
         (local [;; all-paths-from : String -> [Listof Path]
                 ;; All paths from given node to dst
                 (define (all-paths-from n)
                   (map (lambda (p) (cons n p))
                        (all-paths/seen g n dst (cons src seen))))]

         (map-append all-paths-from (neighbors g src)))]))

;; map-append : [X Y] . [X -> [Listof Y]] [Listof X] -> [Listof Y]
;; map a function and append all the list of results
(define (map-append f xs) (foldr append '() (map f xs)))
;; NB: could be more efficient
\end{SaveVerbatim}

\end{document}
